Title

### 2013-03-01 inc/extension/initial_conditions/initial_conditions.tex
start merging andreas' comments on initial conditions section

\section{Determining Appropriate Initial Conditions} \label{sec:initial_conditions}
For a DTEM or UED apparatus, where the electron pulse is produced in a laser-driven photo-electron gun, the implementation of the AG model of Michalik and Sipe \cite{michalik_analytic_2006} requires knowledge of the initial ($ t = 0 $) bunch parameters immediately after generation at the photocathode surface inside the acceleration region of the gun.
For the purposes of this paper, we will make a simple approximation to the behavior of the gun in order to provide generic initial conditions for the electron pulse.

@@

% transverse
Consider a single-photon photoemission process with a spatially cylindrically symmetric incident Gaussian laser beam with Gaussian temporal irradiance profile 
\begin{equation}\label{eq:laser_form}
I ( x , y , t ) = I_{0} \exp \left ( - \frac{ ( x^{2} +y^{2} ) }{ w^{2} } - \frac{ t^{ 2 } }{ \tau^{ 2 } } \right ) \punct{,}
\end{equation}
where $w$ is the half-width 1/e maximum (HW1/eM) of the spatial irradiance distribution, $\tau$ is the HW1/eM pulse duration and $I_{0}$ is the peak pulse irradiance incident on a flat metallic photocathode.
The initial tranverse properties of the beam are easily understood.
The electron pulse's initial spatial variance is simply
\begin{equation}
\sigma_{\smallT } ( 0 ) = ( \Delta x )^{2} = ( \Delta y)^{2} = \frac{ w^{2} }{ 2 } \punct{.}
\end{equation}
A laser pulse of this form has a temporal uncertainty $ \Delta t_{L} = \tau / \sqrt{2} $.

>>>>

\section{Determining Appropriate Initial Conditions} \label{sec:initial_conditions}
For a DTEM or UED apparatus, where the electron pulse is produced in a laser-driven photo-electron gun, the implementation of the AG model of Michalik and Sipe \cite{michalik_analytic_2006} requires knowledge of the initial ($ t = 0 $) bunch parameters immediately after generation at the photocathode surface inside the acceleration region of the gun.
For the purposes of this thesis, we will make a simple approximation to the behavior of the gun in order to provide generic initial conditions for the electron pulse.

@@

% transverse
Consider a single-photon photoemission process with a spatially cylindrically symmetric incident Gaussian laser beam with Gaussian temporal irradiance profile 
\begin{equation}\label{eq:laser_form}
I ( x , y , t ) = I_{0} \exp \left ( - \frac{ ( x^{2} +y^{2} ) }{ w^{2} } - \frac{ t^{ 2 } }{ \tau^{ 2 } } \right ) \punct{,}
\end{equation}
where $w$ is the half-width 1/e maximum (HW1/eM) of the spatial irradiance distribution, $\tau$ is the HW1/eM pulse duration and $I_{0}$ is the peak pulse irradiance incident on a flat metallic photocathode.
The initial tranverse properties of the beam are easily understood.
The electron pulse's initial spatial variance is simply
\begin{equation}
\sigma_{\smallT } ( 0 ) = ( \Delta x )^{2} = ( \Delta y)^{2} = \frac{ w^{2} }{ 2 } \punct{.}
\end{equation}
Similarly, a laser pulse of this form has a temporal uncertainty $ \Delta t_{L} = \tau / \sqrt{2} $.

### 2013-03-01 main.tex
start merging andreas' comments on initial conditions section

Modeling a system as complex as an Ultrafast Electron Microscope is a task too large for one person.
In Chapter \ref{chap:previous_models} I have highlighted some previous efforts at modeling electron pulse evolution.
While these are excellent works in their own right, none provide the complete picture of the evolution of an electron pulse through the entire column.
In the following chapter I will present a model which builds on and extends those individual pieces to form a single model; one which is generic enough to model many different columns and which is computationally fast enough to be used to design and optimize a column.

>>>>

Modeling a system as complex as an Ultrafast Electron Microscope is an enourmous task.
In Chapter \ref{chap:previous_models}, I have highlighted some previous efforts at modeling electron pulse evolution.
While these are excellent works in their own right, none provide the complete picture of the evolution of an electron pulse through the entire column.
In the following chapter, I will present a model which builds on and extends those individual pieces to form a single model; one which is generic enough to model many different columns and is computationally fast enough to be used to design and optimize a column.
